**Title**

### 2018-07-10 manuscript_draft.Rmd
first results in the manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

###DNA isolation and quantification
DNA was isolated before the start of the experiment, first, second and last day of incubation to quantify microbial biomass in the microcosms. Two ml of well mixed liquid solution was sampled and thorougly mixed with two ml of phosphate buffer. The final solution was centrifuged at 4,700 g for ten minutes at 4$^{\circ}C$ and pelet was separated from supernatant. Supernatant was anaylzed for protein concentration (see later). Pellet was resuspended in 0.5 ml and kept deep frozen (-80$^{\circ}C$) until the assay was conducted. 
Cell pelet was bead beated in ethanol solution for 5 minutes to lyse the cells. To isolate DNA from the cell lysate, DNeasy PowerSoil Kit (QIAGEN, Venlo, Netherland) was used. DNA concentration was measured by a Nanodrop meter **_(specification)_**. DNA concentration [@Christensen1993]

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(ggplot2)
library(grid)

theme_min<-theme(axis.text.x=element_text(vjust=0.2, size=14, colour="black"),
                 axis.text.y=element_text(hjust=0.2, size=14, colour="black"),
                 axis.title=element_text(size=14, colour="black"),
                 axis.line=element_line(size=0.5, colour="black"),
                 strip.text=element_text(size=16, face="bold"),
                 axis.ticks=element_line(size=1, colour="black"),
                 axis.ticks.length=unit(-0.05, "cm"),
                 panel.background=element_rect(colour="black", fill="white"),
                 panel.grid=element_line(linetype=0),
                 legend.text=element_text(size=14, colour="black"),
                 legend.title=element_text(size=14, colour="black"),
                 legend.position=c("right"),
                 legend.key.size=unit(1, "cm"),
                 strip.background=element_rect(fill="grey98", colour="black"),
                 legend.key=element_rect(fill="white", size=1.2),
                 legend.spacing=unit(0.5, "cm"),
                 plot.title=element_text(size=28, face="bold", hjust=-0.05))

```

@@

###DNA isolation and quantification
DNA was isolated before the start of the experiment, first, second and last day of incubation to quantify microbial biomass in the microcosms. Two ml of well mixed liquid solution was sampled and thorougly mixed with two ml of phosphate buffer. The final solution was centrifuged at 4,700 g for ten minutes at 4$^{\circ}C$ and pelet was separated from supernatant. Supernatant was anaylzed for protein concentration (see later). Pellet was resuspended in 0.5 ml and kept deep frozen (-80$^{\circ}C$) until the assay was conducted. 
Cell pelet was bead beated in ethanol solution for 5 minutes to lyse the cells. To isolate DNA from the cell lysate, DNeasy PowerSoil Kit (QIAGEN, Venlo, Netherland) was used. DNA concentration was measured by a Nanodrop meter **_(specification)_**. DNA concentration was conversed to microbial biomass carbon using several conversion factors published in literature (see Fig. 1)

@@

##Tables
```{r Tab. 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results='asis'}
#tab1<-rbind(decay_all_results$likelihood, monod_all_results$ll_r, mem_all_results$ll_r,
            #mend_all_results$ll_r, mmem_all_results$ll_r)
#colnames(tab1)<-c("_Log Likelihood_", "_N_", "_R^{2}_", "_AIC_")
#rownames(tab1)<-c("First order decay", "Monod growth", "MEM", "MEND", "MMEM")
#write.csv(tab1, "./tab1.csv")

tab1<-read.csv("tab1.csv")
colnames(tab1)<-c(" ", "_Log Likelihood_", "_N_", "_R\\textsuperscript{2}_", "_AIC_")

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), caption = "_**Table 1:** Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only._")
```

##Figures
```{r Scheme 1, eval=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

ggplot(data.frame(a=0, b=0), aes(a,b))+geom_blank()+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x = element_blank(), axis.line.y = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())+
  geom_rect(aes(xmin=0.8, xmax=1.2, ymin=0.65, ymax=0.95), fill="white", colour="black", lwd=1.2)+
  geom_text(aes(x=1, y=0.8, label="DOC"), size=14)+ylim(0.5,1.5)+xlim(0.5,1.5)+
  geom_text(aes(x=1, y=1.3, label="CO[2]"), size=14, parse = T)+
  geom_text(aes(x=1, y=1.5, label=c("First order decay")), size=11, parse = F, fontface="italic")+
  geom_segment(aes(x=1, y=0.95, xend=1, yend=1.25), lwd=1.2, arrow = arrow(length = unit(0.5, "cm")))

ggplot(data.frame(a=0, b=0), aes(a,b))+geom_blank()+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(),
        panel.background = element_blank(),
        axis.line.x = element_blank(), axis.line.y = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())+
  geom_rect(aes(xmin=1.1, xmax=1.5, ymin=0.65, ymax=0.95), fill="white", colour="black", lwd=1.2)+
  geom_text(aes(x=1.3, y=0.8, label="DOC"), size=14)+ylim(0.5,1.5)+xlim(0.5,1.5)+
  geom_text(aes(x=1.3, y=1.3, label="CO[2]"), size=14, parse = T)+
  geom_text(aes(x=1, y=1.5, label=c("Monod growth")), size=11, parse = F, fontface="italic")+
  geom_segment(aes(x=1.3, y=0.95, xend=1.3, yend=1.25), lwd=1.2, arrow = arrow(length = unit(0.5, "cm")))+
  geom_rect(aes(xmin=0.6, xmax=0.8, ymin=0.65, ymax=0.95), fill="white", colour="black", lwd=1.2)

```

```{r Fig. 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=16, fig.width=9, fig.cap="_**Fig. 1:** Distribution of microbial biomass carbon data as directly measured by the DNA or cellular protein concentration and calculated by different conversion factors published in the literature [@Baart2008; @Beck2018; @VanDuuren2013; @Marstorp2000, @Christensen1993; Christensen1993; @Yokoyama2017; @VanPutten1995; @Henriksen1996; @Hanegraaf2001]. Middle line corresonds to the median, lower and upper hinges to first and third quartile respectively, lower and upper whisker extends from lower and upper hinge to 1.5 time the interquartile range. Note that the x axis of both plots have different scales._"}

#write.csv(conversions, "./fig1.csv")
fig1<-read.csv("fig1.csv")

ggplot(fig1, aes(Reference, Cmic))+geom_boxplot(cex=0.8, aes(colour=Organism), show.legend = F)+
  facet_wrap(~Proxy, scales="free", nrow=2)+coord_flip()+theme_min+theme(axis.title.y = element_blank())+
  ylab(expression(paste("Microbial biomass carbon (", mu, "mol ", ml^{-1},")")))
```
